Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-19 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
added additional comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

>>>>

\textcolor{red}{did we address this comment of the ASE reviewer? ``In some of the equations, the variables are not typed. In CPS some of the variables may belong to continuous domains (real numbers). You need to explain the types for variables and justify that the underlying verification tool supports those types.'' I think we should make it explicit in this section.}
